\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[purple]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.93]{geometry}

\usepackage[unicode]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

\firstname{Arseni}
\familyname{Novikau}
\address{}{Minsk, Belarus}
\mobile{+375 (29) 2015733}
\email{novikov.arsenij@gmail.com}


\begin{document}
\maketitle
\section{Projects}
  \cvline
    {Economical strategy}
    {\url{https://github.com/WhyNovaa/Economical-Strategy}\newline{}
    \textbfgame Development project written in Qt focused on building an economic simulation, highlighting skills in resource management, optimization algorithms, and strategic gameplay mechanics.\newline{}
    }

  \cvline
    {File transferring server}
    {\url{https://github.com/Fugasss/FileTransferingApp_Server}\newline{}
    \textbf
    The server application written in Python that provides functionality for file uploading and downloading via HTTP requests. It is designed for efficient and secure file transfer between devices. The server accepts multipart form data for uploads and supports API-based interaction, making it suitable for integration into various client applications for file sharing or storage solutions.\newline{}
    }
  \cvline
    {File transferring app}
    {\url{https://github.com/WhyNovaa/FileTransferringApp_DesktopClient}\newline{}
    \textbf
    Desktop client application designed to facilitate file transfers between users and a server. The project allows users to upload, download, and manage files through an easy-to-use interface. Written in Rust, it likely focuses on performance and security, making it suitable for handling file transfers reliably and efficiently. This desktop client works alongside the corresponding server component, enabling seamless communication between them for file transfer operations.\newline{}
    }
  \cvline 
    {AutoClicker}
    {\url{https://github.com/WhyNovaa/AutoClicker}\newline{}
    \textbf Desktop application written in Python that automates mouse clicks. The user can configure it to simulate mouse clicks at specific intervals and locations, making it useful for repetitive tasks.\newline{}
    }
  \cvline
    {MineSweeper}
    {\url{https://github.com/WhyNovaa/Minesweeper2.0}\newline{}
    \textbf A C++-based Minesweeper game using Qt for its graphical interface. It features classic Minesweeper mechanics like uncovering and flagging mines.
    }
    
\section{Technical Skills}
\cvline
  {Languages}{C++(STL, Qt), Python, Rust, SQL, Bash}
\cvline 
  {Tools}{Docker, Linux}
\cvline
  {VCS}{Git}
\section {Languages}
\cvline 
  {Russian}{Native}
\cvline 
  {English}{B2}
\section{Education}
  \cventry
    {Nov 2019 - June 2020}
    {Software Development}
    {Computer Academy "CompAs", Orsha, Belarus}
    {}{}{}
  \cventry
    {Sep 2023 - June 2027}
    {Cybersecurity, Bachelor}
    {Belarusian State University
    \newline CS: 9+ marks
    \newline Algorithms and data structures: 9+ marks
    \newline Math: 9+ marks} 
    {}{}{}

\section{On the Internet}
    \cvline{GitHub}{\url{https://github.com/WhyNovaa}}
    \cvline{LinkedIn}{\url{https://www.linkedin.com/in/whynova/}}

\end{document}
